```{r}
library(tidyverse)
library(janitor)
```

To clean the dataset for use in our dashbaord, we need to make the following alterations:

-   Drop unnecessary columns: we will only use `Season`, `No. of Episode (Season)`, `No. of Episode (Overall)` , `Title of the Episode`, `Featuring`, `Also Appearing`, `IMDb Rating` , and `Synopsys`.

-   Rename columns to `snake_case` format

-   Join `Featuring` and `Also Appearing` columns into one column called `characters`, containing all appearing characters in the episode

-   Make new table called `character_appearances` containing all unique characters and their appearances. Modify names for consistency if necessary (eg. change occurences of 'Peter' to 'Peter Griffin' to avoid discrepancies.)

```{r}
# lood in data
family_guy_data <- read_csv('../data/raw/family_guy_dataset.csv')
```

```{r}
# select and rename columns
family_guy_data <- family_guy_data |> 
  select(`No. of Episode (Overall)`,Season, 
         `No. of Episode (Season)`,`Title of the Episode`,
         Featuring,`Also Appearing`,`IMDb Rating`,Synopsys) |> 
  clean_names() |> 
  rename(id = no_of_episode_overall,
         title = title_of_the_episode,
         imdb_rating = im_db_rating,
         synopsis = synopsys)
```

```{r}
# make new character_appearance dataframe
char_appearance <- family_guy_data |> 
  mutate(characters = str_c(featuring,also_appearing,sep=', ')) |> 
  select(id,characters)

# drop character cols from main dataframe
family_guy_data <- family_guy_data |> select(-featuring,-also_appearing)
```

```{r}
# replace first name main character occurances witb full name, for consistency
char_appearance <- char_appearance |> 
mutate(characters = characters |> 
    str_replace_all("\\bPeter(?! Griffin)\\b", "Peter Griffin") |> 
    str_replace_all("\\bLois(?! Griffin)\\b", "Lois Griffin") |> 
    str_replace_all("\\bStewie(?! Griffin)\\b", "Stewie Griffin") |> 
    str_replace_all("\\bMeg(?! Griffin)\\b", "Meg Griffin") |> 
    str_replace_all("\\bChris(?! Griffin)\\b", "Chris Griffin") |> 
    str_replace_all("\\bBrian(?! Griffin)\\b", "Brian Griffin") |> 
    str_replace_all("\\bJoe(?! Swanson)\\b", "Joe Swanson") |> 
    str_replace_all("\\bCleveland(?! Brown)\\b", "Cleveland Brown"))
```

```{r}
# split character strings into individual characters, and unneest
char_appearance <-  char_appearance |> 
  mutate(characters = str_split(characters,', ')) |> unnest(cols = characters)
```

```{r}
# write to dataframe
write_csv
```
